%! Author = omar
%! Date = 2/22/24

% Preamble
\documentclass{article}

% Packages
\usepackage{amsmath} % Include the amsmath package for mathematical commands
\usepackage{xcolor} % Include the xcolor package for coloring text
\usepackage{amsthm} % Include the amsthm package for theorem-like environments

\theoremstyle{definition} % Set the style of the definition environment
\newtheorem{definition}{Definition}[section] % Define a new "definition" environment

% Document
\begin{document}

    \section{Force and Mass}
    This is the content of the first section.

    \subsection{Mass}
    This is a subsection within the first section.

    \begin{definition}[mass]
        The mass of an object is a measure of the object's resistance to change in it's velocity.
    \end{definition}

    \subsubsection{Subsubsection}
    This is a subsubsection within the subsection.

    \section{Newton's First Law}
    This is the content of the second section.

    \begin{definition}[Law 1]
        Every body continues in its state of rest, or in uniform motion in a right [straight] line unless it is compelled to change that state by forces impressed upon it.
    \end{definition}

    The net force $\sum \vec{F}$ excerted on an object is the vector sum of all the individual forces exerted on it by other objects.

    \begin{equation}
        \sum \vec{F} = \vec{F}_1 +\vec{F}_2 + \vec{F}_3 + \dots \label{eq:Net_Force}
    \end{equation}


    The sum of force vectors can be represented as:
    \[
        \vec{F}_{\text{total}} = \sum \vec{F}_i
    \]
    where $\vec{F}_{\text{total}}$ is the total force vector, and $\vec{F}_i$ are individual force vectors.


    Newtons First law in modern terms.

    \begin{definition}[Newton's first law in modern terms]
        If the net force on an object is zero ($\sum \vec{F} = 0$), then the object's acceleration is zero ($\vec{a} = 0$).
    \end{definition}

    \section{Newton's Second Law}
    This is the content of the third section.

    \section{Newton's Third Law}
    This is the content of the fourth section.

    \section{Weight and the Gravitational Force by the Earth}
    This is the content of the fifth section.


\end{document}
